\usefont{OT1}{bch}{b}{n} \normalfont \normalsize \textsc{School of random department names} \\ [25pt] \horrule{0.5pt} \\[0.4cm] \huge Efficient modeling of timeouts in PRISM \\ \horrule{2pt} \\[0.5cm]

### 2018-06-22 Report/notes.tex
put notation in tool paper + change template (but missing bib files => need to add it later

	\end{abstract}
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%SECTION1%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\begin{figure}
	\centering
	\includegraphics[width=15cm]{picture/New_model/distance_constant_1E-5.png}
	\caption{Infinite Distance of distribution of the SSP computation between the event model and the PTF model using hybrid engine versus the PTF parameter k,$t=0.1$,median $\lambda$,$\epsilon=10^{-5}$}
	\label{fig:dist_const_1E-5}
\end{figure}

@@

\begin{figure}
	\centering
	\includegraphics[width=17cm]{picture/New_model/diff_explicit_dynamic.png}
	\caption{Absolute Difference between SSP of event model and of SSP PTF model using explicit engine versus state of queue,$t=1$,median $\lambda$,$\epsilon=10^{-5}$}
	\label{fig:dist_dynamic_explicit}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=17cm]{picture/New_model/diff_hybrid_dynamic.png}
	\caption{Absolute Difference between SSP of event model and of SSP PTF model using hybrid engine versus state of queue,$t=1$,median $\lambda$,$\epsilon=10^{-5}$}
	\label{fig:dist_dynamic_hybrid}
\end{figure}

\subsection{more data}
\begin{figure}
	\centering
	\includegraphics[width=17cm]{picture/New_model/distance_versus_k.png}
	\caption{infinity norm distance between SSP of event model with 1E-10 epsilon termination and SSP of event model and PTH model using hybrid and explicit,$t=1$,median $\lambda$,$\epsilon=10^{-5}$}
	\label{fig:dist_versus_k}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=16cm]{picture/New_model/performance_versus_k.png}
	\caption{Computation time for different values of $k$. For about $k>200$, GSMP implementation starts outperforming all phase-typed computations, despite the GSMP implementation being relatively poorly optimized.}
	\label{fig:performance}
\end{figure}

>>>>

	\end{abstract}
	\keywords{CTMC}

	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%SECTION1%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\begin{figure}
	\centering
	\includegraphics[width=15cm]{picture/New_model/1E-5/distance_constant_1E-5.png}
	\caption{Infinite Distance of distribution of the SSP computation between the event model and the PTF model using hybrid engine versus the PTF parameter k,$t=0.1$,median $\lambda$,$\epsilon=10^{-5}$}
	\label{fig:dist_const_1E-5}
\end{figure}

@@

\begin{figure}
	\centering
	\includegraphics[width=17cm]{picture/New_model/1E-5/diff_explicit_dynamic.png}
	\caption{Absolute Difference between SSP of event model and of SSP PTF model using explicit engine versus state of queue,$t=1$,median $\lambda$,$\epsilon=10^{-5}$}
	\label{fig:dist_dynamic_explicit}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=17cm]{picture/New_model/1E-5/diff_hybrid_dynamic.png}
	\caption{Absolute Difference between SSP of event model and of SSP PTF model using hybrid engine versus state of queue,$t=1$,median $\lambda$,$\epsilon=10^{-5}$}
	\label{fig:dist_dynamic_hybrid}
\end{figure}

\subsection{more data}
\begin{figure}
	\centering
	\includegraphics[width=17cm]{picture/New_model/1E-5/distance_dynamic_1E-5.png}
	\caption{infinity norm distance between SSP of event model with 1E-10 epsilon termination and SSP of event model and PTH model using hybrid and explicit,$t=1$,median $\lambda$,$\epsilon=10^{-5}$}
	\label{fig:dist_versus_k}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=16cm]{picture/New_model/1E-5/performance_dynamic.png}
	\caption{Computation time for different values of $k$. For about $k>200$, GSMP implementation starts outperforming all phase-typed computations, despite the GSMP implementation being relatively poorly optimized.}
	\label{fig:performance}
\end{figure}

### 2018-06-22 Report/tool_paper.tex
put notation in tool paper + change template (but missing bib files => need to add it later

%% This is file `elsarticle-template-1-num.tex',
%%
%% Copyright 2009 Elsevier Ltd
%%
%% This file is part of the 'Elsarticle Bundle'.
%% ---------------------------------------------
%%
%% It may be distributed under the conditions of the LaTeX Project Public
%% License, either version 1.2 of this license or (at your option) any
%% later version.  The latest version of this license is in
%%    http://www.latex-project.org/lppl.txt
%% and version 1.2 or later is part of all distributions of LaTeX
%% version 1999/12/01 or later.
%%
%% Template article for Elsevier's document class `elsarticle'
%% with numbered style bibliographic references
%%
%% $Id: elsarticle-template-1-num.tex 149 2009-10-08 05:01:15Z rishi $
%% $URL: http://lenova.river-valley.com/svn/elsbst/trunk/elsarticle-template-1-num.tex $
%%
\documentclass[article,12pt]{elsarticle}

%% Use the option review to obtain double line spacing
%% \documentclass[preprint,review,12pt]{elsarticle}

%% Use the options 1p,twocolumn; 3p; 3p,twocolumn; 5p; or 5p,twocolumn
%% for a journal layout:
%% \documentclass[final,1p,times]{elsarticle}
%% \documentclass[final,1p,times,twocolumn]{elsarticle}
%% \documentclass[final,3p,times]{elsarticle}
%% \documentclass[final,3p,times,twocolumn]{elsarticle}
%% \documentclass[final,5p,times]{elsarticle}
%% \documentclass[final,5p,times,twocolumn]{elsarticle}

%% The graphicx package provides the includegraphics command.
\usepackage{graphicx}
%% The amssymb package provides various useful mathematical symbols
\usepackage{amssymb}
%% The amsthm package provides extended theorem environments
%% \usepackage{amsthm}
\usepackage{pgf}
\usepackage{tikz}
\usetikzlibrary{arrows,automata}
\usetikzlibrary{chains,shapes.multipart}

\usepackage{listings}
\usepackage{color}
%% PRISM CODE LISTING 
\definecolor{dkgreen}{rgb}{0,0.6,0}
\definecolor{gray}{rgb}{0.5,0.5,0.5}
\lstset{frame=tb,
	language=Java,
	aboveskip=1mm,
	belowskip=1mm,
	showstringspaces=false,
	columns=flexible,
	basicstyle={\fontsize{8.8}{8.5}\ttfamily},
	numbers=none,
	numberstyle=\tiny\color{gray},
	keywordstyle=\color{blue},
	commentstyle=\color{dkgreen},
	breaklines=true,
	breakatwhitespace=true,
	tabsize=3,
	morekeywords={event, gsmp, dirac, exponential, uniform, weibull, erlang,
		module, init, rewards, endrewards, label, true, endmodule}
}

\usepackage{hyperref}
\hypersetup{
    colorlinks=true,       % false: boxed links; true: colored links
    linkcolor=red,          % color of internal links 
    urlcolor=cyan           % color of external links
}

\usepackage{float}

%% The lineno packages adds line numbers. Start line numbering with
%% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
%% for the whole article with \linenumbers after \end{frontmatter}.
\usepackage{lineno}

%% natbib.sty is loaded by default. However, natbib options can be
%% provided with \biboptions{...} command. Following options are
%% valid:

%%   round  -  round parentheses are used (default)
%%   square -  square brackets are used   [option]
%%   curly  -  curly braces are used      {option}
%%   angle  -  angle brackets are used    <option>
%%   semicolon  -  multiple citations separated by semi-colon
%%   colon  - same as semicolon, an earlier confusion
%%   comma  -  separated by comma
%%   numbers-  selects numerical citations
%%   super  -  numerical citations as superscripts
%%   sort   -  sorts multiple citations according to order in ref. list
%%   sort&compress   -  like sort, but also compresses numerical citations
%%   compress - compresses without sorting
%%
%% \biboptions{comma,round}

% \biboptions{}

% \journal{Journal Name}

\begin{document}

\begin{frontmatter}

%% Title, authors and addresses

\title{Efficient modeling of timeouts in PRISM}

%% use the tnoteref command within \title for footnotes;
%% use the tnotetext command for the associated footnote;
%% use the fnref command within \author or \address for footnotes;
%% use the fntext command for the associated footnote;
%% use the corref command within \author for corresponding author footnotes;
%% use the cortext command for the associated footnote;
%% use the ead command for the email address,
%% and the form \ead[url] for the home page:
%%
%% \title{Title\tnoteref{label1}}
%% \tnotetext[label1]{}
%% \author{Name\corref{cor1}\fnref{label2}}
%% \ead{email address}
%% \ead[url]{home page}
%% \fntext[label2]{}
%% \cortext[cor1]{}
%% \address{Address\fnref{label3}}
%% \fntext[label3]{}

%% use optional labels to link authors explicitly to addresses:
%% \author[label1,label2]{<author name>}
%% \address[label1]{<address>}
%% \address[label2]{<address>}

\author{John Smith}

\address{California, United States}

@@

\begin{keyword}
PRISM model checker \sep CTMC \sep deterministic timeout \sep phase-type distribution \sep modeling \sep analysis
%% keywords here, in the form: keyword \sep keyword

@@

\end{keyword}

\end{frontmatter}

%%
%% Start line numbering here if you want
%%
\linenumbers

@@

\begin{figure}[H]
\begin{center}
\includegraphics[trim=0.3cm 0cm 0cm 1.35cm,width=15cm, clip]{distance_constant_1E-6.png}
\end{center}
\caption{Maximum distance (infinity norm) of the steady-state probabilities from the reference high-precision ACTMC ($10^{-20}$) against various values of $k$ for default absolute termination epsilon $\epsilon = 10^{-6}$. ACTMC results for $\epsilon = 10^{-6}$ are also compared to the reference and have a smaller error than the declared $\epsilon = 10^{-6}$.}
\label{fig:distance_constant_standard_constant_kappa}
\end{figure}

@@

\begin{figure}[H]
\begin{center}
\includegraphics[trim=0.2cm 0cm 0cm 1.35cm,width=15cm, clip]{distance_constant_1E-10.png}
\end{center}
\caption{Maximum distance (infinity norm) of the steady-state probabilities from the reference high-precision ACTMC ($10^{-20}$) against various values of $k$ for lowered absolute termination epsilon $\epsilon = 10^{-10}$. ACTMC results for $\epsilon = 10^{-10}$ are also compared to the reference and have a smaller error than the declared $\epsilon = 10^{-10}$.}
\label{fig:distance_constant_1E-10_constant_kappa}
\end{figure}

@@

\begin{figure}[H]
\begin{center}
\includegraphics[trim=0.2cm 0cm 0cm 1.35cm,width=15cm, clip]{distance_dynamic_1E-10.png}
\end{center}
\caption{Maximum distance (infinity norm) of the steady-state probabilities from the reference high-precision ACTMC ($10^{-20}$) against various values of $k$ for lowered and adjusted absolute termination epsilon $\epsilon = 10^{-10}$. ACTMC results for $\epsilon = 10^{-10}$ are also compared to the reference and have a smaller error than the declared $\epsilon = 10^{-10}$.}
\label{fig:distance_dynamic_1E-10_constant_kappa}
\end{figure}

@@

\begin{figure}[H]
\begin{center}
\includegraphics[trim=0.2cm 0cm 0cm 1.35cm,width=15cm, clip]{performance_dynamic.png}
\end{center}
\caption{Time of computation in seconds of the steady-state probabilities against various values of $k$ for lowered and adjusted absolute termination epsilon $\epsilon = 10^{-10}$, i.e. corresponding to the data shown in Figure \ref{fig:distance_dynamic_1E-10_constant_kappa}. The computation of our PRISM ACTMC is constant in regards to $k$ because it does not use phase-type fitting. }
\label{fig:performance_dynamic}
\end{figure}

@@

\end{document}

%%
%% End of file `elsarticle-template-1-num.tex'.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% LaTeX Example: Project Report
%
% Source: http://www.howtotex.com
%
% Feel free to distribute this example, but please keep the referral
% to howtotex.com
% Date: March 2011 
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% How to use writeLaTeX: 
%
% You edit the source code here on the left, and the preview on the
% right shows you the result within a few seconds.
%
% Bookmark this page and share the URL with your co-authors. They can
% edit at the same time!
%
% You can upload figures, bibliographies, custom classes and
% styles using the files menu.
%
% If you're new to LaTeX, the wikibook is a great place to start:
% http://en.wikibooks.org/wiki/LaTeX
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Edit the title below to update the display in My Documents
%\title{Project Report}
%
%%% Preamble
\documentclass[paper=a4, fontsize=11pt]{scrartcl}
\usepackage[T1]{fontenc}
\usepackage{fourier}
\usepackage{hyperref}

\hypersetup{
	colorlinks=true,       % false: boxed links; true: colored links
	linkcolor=red,          % color of internal links 
	urlcolor=cyan           % color of external links
}

\usepackage[english]{babel}															% English language/hyphenation
\usepackage[protrusion=true,expansion=true]{microtype}	
\usepackage{amsmath,amsfonts,amsthm} % Math packages
\usepackage[pdftex]{graphicx}	
\usepackage{url}
\usepackage{xcolor}

%%% Custom sectioning
\usepackage{sectsty}
\allsectionsfont{\centering \normalfont\scshape}
\usepackage{tikz}
\usetikzlibrary{chains,shapes.multipart}
\usepackage{pgf}
\usepackage{tikz}
\usetikzlibrary{arrows,automata}

%%% Custom headers/footers (fancyhdr package)
\usepackage{fancyhdr}
\pagestyle{fancyplain}
\fancyhead{}											% No page header
\fancyfoot[L]{}											% Empty 
\fancyfoot[C]{}											% Empty
\fancyfoot[R]{\thepage}									% Pagenumbering
\renewcommand{\headrulewidth}{0pt}			% Remove header underlines
\renewcommand{\footrulewidth}{0pt}				% Remove footer underlines
\setlength{\headheight}{13.6pt}

%%% Equation and float numbering
\numberwithin{equation}{section}		% Equationnumbering: section.eq#
\numberwithin{figure}{section}			% Figurenumbering: section.fig#
\numberwithin{table}{section}				% Tablenumbering: section.tab#

%%% Maketitle metadata
\newcommand{\horrule}[1]{\rule{\linewidth}{#1}} 	% Horizontal rule

\title{
	%\vspace{-1in} 	
	\usefont{OT1}{bch}{b}{n}
	\normalfont \normalsize \textsc{School of random department names} \\ [25pt]
	\horrule{0.5pt} \\[0.4cm]
	\huge Efficient modeling of timeouts in PRISM \\
	\horrule{2pt} \\[0.5cm]
}
\author{
	\normalfont 								\normalsize
	Thomas Mari, M\'{a}rio Uhr\'{i}k\\[-3pt]		\normalsize
	\today
}
\date{}

\usepackage{listings}
\usepackage{color}
\usepackage{float}

%% BEGIN PRISM CODE LISTING 
\definecolor{dkgreen}{rgb}{0,0.6,0}
\definecolor{gray}{rgb}{0.5,0.5,0.5}

\lstset{frame=tb,
	language=Java,
	aboveskip=1mm,
	belowskip=1mm,
	showstringspaces=false,
	columns=flexible,
	basicstyle={\fontsize{8.8}{8.5}\ttfamily},
	numbers=none,
	numberstyle=\tiny\color{gray},
	keywordstyle=\color{blue},
	commentstyle=\color{dkgreen},
	breaklines=true,
	breakatwhitespace=true,
	tabsize=3,
	morekeywords={event, gsmp, dirac, exponential, uniform, weibull, erlang,
		module, init, rewards, endrewards, label, true, endmodule}
}

%%% Begin document
\begin{document}
	\maketitle

@@

	\begin{description}

		\item[Keywords:] 	PRISM model checker ; CTMC ; deterministic timeout ; phase-type distribution ; modeling ; analysis

	\end{description}

	%% keywords here, in the form: keyword \sep keyword

@@

@@

	\begin{figure}[H]
		\begin{center}
			\includegraphics[trim=0.3cm 0cm 0cm 1.35cm,width=15cm, clip]{picture/New_model/1E-6/distance_constant_1E-6.png}
		\end{center}
		\caption{Maximum distance (infinity norm) of the steady-state probabilities from the reference high-precision ACTMC ($10^{-20}$) against various values of $k$ for default absolute termination epsilon $\epsilon = 10^{-6}$. ACTMC results for $\epsilon = 10^{-6}$ are also compared to the reference and have a smaller error than the declared $\epsilon = 10^{-6}$.}
		\label{fig:distance_constant_standard_constant_kappa}
	\end{figure}

@@

	\begin{figure}[H]
		\begin{center}
			\includegraphics[trim=0.2cm 0cm 0cm 1.35cm,width=15cm, clip]{picture/New_model/1E-10/distance_constant_1E-10.png}
		\end{center}
		\caption{Maximum distance (infinity norm) of the steady-state probabilities from the reference high-precision ACTMC ($10^{-20}$) against various values of $k$ for lowered absolute termination epsilon $\epsilon = 10^{-10}$. ACTMC results for $\epsilon = 10^{-10}$ are also compared to the reference and have a smaller error than the declared $\epsilon = 10^{-10}$.}
		\label{fig:distance_constant_1E-10_constant_kappa}
	\end{figure}

@@

	\begin{figure}[H]
		\begin{center}
			\includegraphics[trim=0.2cm 0cm 0cm 1.35cm,width=15cm, clip]{picture/New_model/1E-10/distance_dynamic_1E-10.png}
		\end{center}
		\caption{Maximum distance (infinity norm) of the steady-state probabilities from the reference high-precision ACTMC ($10^{-20}$) against various values of $k$ for lowered and adjusted absolute termination epsilon $\epsilon = 10^{-10}$. ACTMC results for $\epsilon = 10^{-10}$ are also compared to the reference and have a smaller error than the declared $\epsilon = 10^{-10}$.}
		\label{fig:distance_dynamic_1E-10_constant_kappa}
	\end{figure}

@@

	\begin{figure}[H]
		\begin{center}
			\includegraphics[trim=0.2cm 0cm 0cm 1.35cm,width=15cm, clip]{picture/New_model/1E-6/performance_dynamic.png}
		\end{center}
		\caption{Time of computation in seconds of the steady-state probabilities against various values of $k$ for lowered and adjusted absolute termination epsilon $\epsilon = 10^{-10}$, i.e. corresponding to the data shown in Figure \ref{fig:distance_dynamic_1E-10_constant_kappa}. The computation of our PRISM ACTMC is constant in regards to $k$ because it does not use phase-type fitting. }
		\label{fig:performance_dynamic}
	\end{figure}

@@

\end{document}\\
